Perimeter Control of Swarms

### 2019-01-08 paper.tex
More updates

Ant-colony research requires directional agents to implement aforgaing behaviour, the goal is usually to find energy sources and return them to a common base. The initial coordination of the direction of agents in a foraging scenario is randomised. The control component is applied using several different techniques including pheremone trails~\cite{JRD:03,RGJHR:08,VBBLO:15,STZZW:13,SK:16} . Gazi and Passino examined foraging algorithms to measure their stability but the swarms used a random movement approach in the foraging behaviour~\cite{GP:04a}. Hoff et al. used a hybrid approac to their coordination wich does include a directional bias. They achieve this by allowing agents to become beacons~\cite{HSWN:10}. As such they are adding a destination bias to local agent movemnents. However, the mechanism requires local communications and all agents are using a communications infrastructure to identify the beacons. Lee et al. also present a goal-based scenario that utilises GPS however, it is only used by individual agents when returning to a "storehouse"~\cite{LAA:13}.

Alternative approaches also include using a global coordination through unique agent markings and a series of cameras that employ image recognition to coordinate agents to a goal. Furci et al. uses this technique to coordinate crazyfly quadcopters~\cite{FCNSM:15}. This same technique is often used in football playing robots for the `RoboCup' where each team is in effect a swarm~\cite{LL:09}. This technique is shown by Lupashin et al. in their design of a `Flying machine area'~\cite{LSHD:11} and is used by Brescianini et al. when coordinating two quadcopters to pass a pole between each other and balnce it~\cite{BHD:13}. This same technique is also used by Augugliaro et al. to calculate quadcopter trajectories~\cite{ASD:12}.

The use of GPS as a mechanism to coordinate agents within in a swarm is common~\cite{SG:15,TG:12,AZHMJJM:12,MPYV:02,LAA:13,RRSTM:15}. However, the usual approach is to have a directional bias applied to all the agents within the swarm.

>>>>

Ant-colony research requires directional agents to implement aforgaing behaviour, the goal is usually to find energy sources and return them to a common base. The initial coordination of the direction of agents in a foraging scenario is randomised. The control component is applied using several different techniques including pheromone trails~\cite{JRD:03,RGJHR:08,VBBLO:15,STZZW:13,SK:16} . Gazi and Passino examined foraging algorithms to measure their stability but the swarms used a random movement approach in the foraging behaviour~\cite{GP:04a}. Hoff et al. used a hybrid approac to their coordination wich does include a directional bias. They achieve this by allowing agents to become beacons~\cite{HSWN:10}. As such they are adding a destination bias to local agent movemnents. However, the mechanism requires local communications and all agents are using a communications infrastructure to identify the beacons. Lee et al. also present a goal-based scenario that utilises GPS however, it is only used by individual agents when returning to a "storehouse"~\cite{LAA:13}.

Alternative approaches also include using a global coordination through unique agent markings and a series of cameras that employ image recognition to coordinate agents to a goal. Furci et al. uses this technique to coordinate crazyfly quadcopters~\cite{FCNSM:15}. This same technique is often used in football playing robots for the `RoboCup' where each team is in effect a swarm~\cite{LL:09}. This technique is shown by Lupashin et al. in their design of a `Flying machine area'~\cite{LSHD:11} and is used by Brescianini et al. when coordinating two quadcopters to pass a pole between each other~\cite{BHD:13}. This same technique is also used by Augugliaro et al. to calculate quadcopter trajectories~\cite{ASD:12} and to coordinate `knot-tying' quadcopters~\cite{AZMD:15}.

The use of GPS as a mechanism to coordinate agents within in a swarm is common~\cite{SG:15,TG:12,AZHMJJM:12,MPYV:02,LAA:13,RRSTM:15}. However, the usual approach is to have a directional bias applied to all the agents within the swarm. This paper proposes an alternative approach to directional coordination by identifying a subset of agents obtaining a directional bias an all other agents maintaining relative position within the swarm construct.
